This deliverable describes the outcomes of the activities carried out in tasks T4.3 (``Ranking matching results'') and T4.4 (``Implementation of the algorithms, application and evaluation''). In particular, T4.3 covers the description of profiling mechanisms and privacy-aware algorithms  %including those 
for the searching and ranking of peers. On the other hand, T4.4 focuses on the implementation and integration of these mechanisms into the overall SmartSociety platform as well as the definition of plans for evaluating the methods and mechanisms defined.

During the second year of the project, the WP4 worked on the refinement of models for data and knowledge representation and for privacy-aware storage, as well as the definition of mechanisms for matching atomic-tasks with peers and ranking matching results. 
As such, the main outcome was the definition of the \emph{Peer Manager (PM)} component as a privacy-aware information service for all peer-related information in the SmartSociety platform. This definition included also the specification of a privacy-by-design architecture for the PM. The results of this work were reported in~\cite{D4.2}.
Although the focus of year 2 was on the definition of models and mechanisms, an initial prototype of the PM was also developed during such period and the early reports of this implementation was included in the aforementioned deliverable. 
%deliverable D4.2.

The main objectives of WP4 in the period M25-M30 have been:
\begin{enumerate}
\item To enhance and extend the models and mechanisms described in~\cite{D4.2};
\item To complete the implementation and integration of the key PM functionality;
\item To define a set of evaluation procedures for assessing the ability of the PM to match the requirements for HDA-CASs. 
\end{enumerate}

%With respect to the latter point, it is worth remarking that the execution of the actual evaluation and assessment will take place during the second half of 2015. 
%In this regard, it is important to note that this deliverable covers only partially the work towards the above mentioned objectives (i.e., until M30). As a consequence, only the definition of a plan for evaluation is presented in this document while its execution is planned for the second half of year 3 and the report of the evaluation results will be presented in the next deliverable.

These objectives have been mapped to the structure of the deliverable, whose remainder is organized as follows. Sec.~\ref{sec:profiling} describes the PM model enhancements and the support added for privacy-aware mechanisms. Sec.~\ref{sec:matching_ranking} describes the search, matching and ranking methods implemented and integrated in the first half of year 3. Evaluation methods and procedures are described in Sec.~\ref{sec:evaluation}. A description of the current integration of PM in the overall SmartSociety platform is included in Sec.~\ref{sec:integration}. Sec.~\ref{sec:concl} concludes the report with a roadmap for the last 18 months of project activities.