The following is a set of questions that form part of WP4's exploratory survey. Notice that because of the generality of these questions and how early they are presented within the evaluation strategy presented in Sec.~\ref{sec:evaluation}, rather than a full evaluation exercise (from which results for WP4 or the project may be extracted) this is more of an exploratory survey aimed to inform and adjust further evaluation activities.

\emph{First part.}
%Post-questionnaire for evaluating PETs

\begin{enumerate}
\item How much time will you spend at configuring / learning the system? 
	\begin{itemize}
	\item Very little
	\item Some time
	\item Lot of time, I like to understand every detail and be in control
	\item other: 
	\end{itemize}
\item In your opinion, was your data well protected when you tried to achieve a task? 
	\begin{itemize}
	\item Yes
	\item I wasn't concerned about that
	\item No
	\item other:
	\end{itemize}
\item Are you comfortable with the information that others find out about you when you tried to achieve a task? 
	\begin{itemize}
	\item No, I want to be completely anonymous
	\item Partially, I would like to share less information
	\item Yes, it was fine
	\item I might easily share more information to allow drivers/commuters to know me better
	\item other:
	\end{itemize}
\item Were you aware of who has access to your information after you completed the task?
	\begin{itemize}
	\item Yes
	\item No
	\item other:
	\end{itemize}
\item How secure, in relation with security of your information, do you feel after having completed the task? 
	\begin{itemize}
	\item Very secure
	\item Secure, I trust the system
	\item I wasn't concerned about that
	\item Insecure
	\item Very insecure 
	\end{itemize}
\end{enumerate}
	

\emph{Second part}
%PET-USES questionnaire

Please use the scale below to show to what extent you disagree or agree with the statements that follow.
\begin{enumerate}
\item Strongly disagree
\item Disagree
\item Neither agree nor disagree
\item Agree
\item Strongly agree
\end{enumerate}

\begin{itemize}
%Data Management
\item I get a clear view of my personal data from the system [~~~]
\item I find managing and organising my personal data easy with this system [~~~]
\item I find keeping track of various usernames and passwords is easy with this system [~~~]

%PrivPrefs
\item I find easy to use the settings for how much or how little data to be released with this system [~~~]
\item I will  find useful if the system helps me understand the effects of different privacy settings [~~~]
\item I would feel safer if I know that I will be notified by the system when I'm about to release more personal data than my chosen preference [~~~]

%Data Release
\item I know what personal information I'm releasing when I’m using this system [~~~]
\item I like to have control over how much or how little data to release in a given transaction [~~~]
\item The system makes it easy to decide how much or how little data to release in a given transaction [~~~]
\item It is clear from the system to understand who will receive my data [~~~]

%History
\item I can easily find out who has received my personal data with this system [~~~]
\item I want to get a good view of who knows what about me from this system [~~~]
\item I can easily see how much I’ve used a particular user name with this system [~~~]
\end{itemize}
